%!TEX TS-program = xelatex
\documentclass[]{friggeri-jj-cv}
\usepackage{wrapfig}
\addbibresource{bibliography.bib}
\begin{document}

% In the aside, each new line forces a line break
\begin{aside}
  \section{languages}
    Bilingual Spanish/English
    B2 Italian
    Spoken French
    German, Dutch notions
  \section{programming}
  {\color{red} \large $\varheartsuit$} Agile mindset
  {\color{red} $\varheartsuit$} Raku \& Perl
  {\color{red} $\varheartsuit$} JavaScript/{\tt node.js} \& TypeScript/Deno;
  R, Python, Go
    Lua, Ruby, shell, CSS3 \& HTML5, Rust, Ansible.
  \end{aside}

\section{TL;DR}

Senior software engineer with 10+ years developing experience, very strong
technical documentation skills, 10+ years Perl, JavaScript experience, team oriented and
very proactive.

\section{interests}

Evolutionary algorithms, complex networks, social networks, emerging
computing, literary engineering, distributed computing, stealth
computing, computational intelligence in games, machine learning,
repository mining, CI/CD/automation engineering, agile programming,
higher education, platform engineering, open source.

\section{education}

\begin{entrylist}
  \entry
    {Before 2000}
    {Ph.D. {\normalfont in Physics} magna cum laude}
    {University in Spain}
    {\emph{Evolutionary neural networks}}
  \entry
    {Before 2000}
    {M.Sc. {\normalfont in Physics} magna cum laude}
    {University in Spain}
    {Majoring in Physics, Specialization in Theoretical Physics}
  \entry
    {Before 2000}
    {Avg B+}
    {University of Granada}
    {B. Sc. in Physics}
\end{entrylist}

\section{experience}

My main job has always been as a researcher and (since 2000+ tenured) professor
at a university. I have also held part-time positions in a company, for a short
period of time, as well as consulting gigs with different, mainly local,
companies. From May 2021 to November 2022 I have been consulting as senior
software engineer at a German Startup.

More than 20 year experience as an open source developer in different languages,
mainly Perl and JavaScript.

In the last years I've volunteered to
help with \href{https://raku.org}{Raku programming language}, mainly creating
and managing the documentation (until May 2022).

\begin{entrylist}
    \entry
    {2017}
    {Member}
    {Microsoft Technical Advisory Group, Cloud CLI \& SDK Tools}
    {1-year position, for consultations on the state and evolution of
      cloud tools}
    \entry
    {April-May '18}
    {Grantee}
    {The Perl Foundation}
    {2-month grant to work on the Raku documentation}
    \entry
    {2018-2022}
    {Documenter-in-chief}
    {Raku}
    {Documentation in Raku is a separate effort from
      development. Being in charge of the documentation obviously
      writing the documentation, but also working with other
      volunteers to improve it as well as in the tooling to test and
      deploy the documentation}

        \entry
    {2020-22}
    {Steering Council}
    {Raku}
    {Elected as part of the 7 member Steering Council, which is the
      last resort for solving problems and disputes in the Raku
      community, and acts as {\em product owner} of the language}
    \entry
    {2021-22}
    {Senior Software Engineer}
    {German Startup}
    {Collaboration as an external consultant through an university
      knowledge transfer contract}

\end{entrylist}

\section{books}

Several technical books on Raku, Python, Javascript, using git and working with
the cloud in English or Spanish.


\section{awards}

\begin{entrylist}
    \entry
    {February 2019}
    {\href{https://summerofcode.withgoogle.com/organizations/4713351599357952/}{Google Summer of Code funding}}
    {\href{https://www.perlfoundation.org/}{The Perl Foundation}}
    {Participation in the selection of ideas, mentors and students
      participating in GSoC, as well as mentoring some projects}

\end{entrylist}


\section{libraries and other released software}

Release and curation of \begin{itemize}
\item 20+ packages in the Perl ecosystem, CPAN
\item 20+ packages in the Raku ecosystem, raku.land
\item 2 items in the Deno ecosystem, deno.land
\item 2 items in the JavaScript ecosystem, npm
\item Maintaining extra-official container images for Raku
\item Several widely used GitHub actions released in the Github Actions marketplace.
\end{itemize}

\end{document}
